Master Thesis

### 2013-06-17 gacg.tex
Fixing mistakes post-print

It is easy to see that the newly introduced pangraphical languages solve
all of the counter-intuitive quirks of object languages that we
discussed in this subsection.

>>>>

It is easy to see that the newly introduced pangraphical languages solve
all of the counter-intuitive quirks of extrinsic languages that we
discussed in this subsection.
